Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
Let's not talk about Hall sets
Search space size

\Cref{figure:ids} demonstrates that this is effective in practice: we show the amount of domain
reduction we can achieve at the top of search by using invariants and a fixed $k$, compared to the
search space size for the maximum common induced subgraph problem. (The results on the non-induced
version show a similar but slightly weaker trend.)

@@

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator
\citep{DBLP:conf/aaai/Regin94} which guarantees generalised arc consistency. Because we use multiple
wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
more than once. ?? A few sentences on how this works. It can easily be seen that this propagator
will always find Hall sets or failed Hall sets of size zero or one, but it may miss larger sets.
This propagation could create new effectively-unit domains; if so, we loop.

>>>>

\Cref{figure:ids} demonstrates that this is effective in practice: we show the amount of domain
reduction we can achieve at the top of search by using invariants and a fixed $k$, compared to the
search space size for the maximum common induced subgraph problem. (The results on the non-induced
version show a similar but slightly weaker trend.) We look at the product of the domain sizes,
rather than the number of eliminations, as this better reflects the number of combinations remaining
to be considered.

@@

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator
\citep{DBLP:conf/aaai/Regin94} which guarantees generalised arc consistency. Because we use multiple
wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
more than once. This propagation could create new effectively-unit domains; if so, we loop.
